### 2014-01-13 thesis/src/chapters/chapter-7-evaluation.tex
Thesis: changed colours

\begin{table}
  \centering
  \begin{tabular}{ | l | l | l | l | }
    \hline                        
    Name & CPU & RAM & HD \\
    \hline
    (device) Desktop        & Intel(R) Core(TM) i5-2500 CPU @ 3.30GHz & 8GB & 1TB \\
    (device) Node1        & AMD Athlon\texttrademark 64 X2 Dual Core, 2000MHz & 3GB & 160GB \\
    (device) Node3        & AMD Sempron(tm) Processor 3000+ & 2.5GB & 160GB \\
    (device) Node4        & AMD Duron(tm) Processor 1GHz& 2.5GB & 60GB \\
    (virtual machine) Frontend\{1,2\}  & 1 CPU & 512MB & 10GB \\
    \hline  
  \end{tabular}
  \caption{Configuration of hardware/virtual machines used during tests}
  \label{tbl:test-deployment-time-common-hardware-configuration}
\end{table}

@@

\begin{table}
  \centering
  \begin{tabular}{ | c | c | c | c | }
    \hline                        
    & CP-1 & CP-2 & CP-3 \\
    \hline
    java      & 150 & 120 & 180 \\
    ruby      & 220 & 290 & 250 \\
    postgres  & 320 & 240 & 290 \\
    python    & 200 & 260 & 180 \\
    amqp      & 330 & 390 & 285 \\
    \hline  
  \end{tabular}
  \caption{Price for a stack in the given cloud provider}
  \label{tbl:test-service-deployment-cost}
\end{table}

@@

\begin{table}
  \centering
  \begin{tabular}{ c  c  c }
    \hline
    & \multicolumn{2}{c}{Solution} \\
    \cline{2-3}
    Instance no & Cloud-SAP & Carina \\
    \hline
    2 & 198.0 & 158.7 \\
    3 & 261.72 & 208.1 \\
    4 & 294.38 & 230.6 \\
    \hline
  \end{tabular}
  \caption{Average deployment time for the service with the various number of VMs used for the whole environment}
  \label{tbl:test-service-deployment-time}
\end{table}

>>>>

\begin{table}
  \centering
  \begin{tabular}{ l l l l l }
    \specialrule{.1em}{.05em}{.05em}                  
    \textbf{Name} & \textbf{VM} & \textbf{CPU} & \textbf{RAM} & \textbf{HD} \\
    \specialrule{.1em}{.05em}{.05em} 
     Desktop   &    & Intel(R) Core(TM) i5-2500 CPU @ 3.30GHz & 8GB & 1TB \\ \hline
     Node1   &     & AMD Athlon\texttrademark 64 X2 Dual Core, 2000MHz & 3GB & 160GB \\ \hline
     Node3  &      & AMD Sempron(tm) Processor 3000+ & 2.5GB & 160GB \\ \hline
     Node4  &      & AMD Duron(tm) Processor 1GHz& 2.5GB & 60GB \\ \hline
     Frontend\{1,2\} & \checkmark & 1 CPU & 512MB & 10GB \\
    \hline  
  \end{tabular}
  \caption{Configuration of hardware/virtual machines used during tests}
  \label{tbl:test-deployment-time-common-hardware-configuration}
\end{table}

@@

\begin{table}
  \centering
  \begin{tabular}{ c  c  c  c  }
    \specialrule{.1em}{.05em}{.05em}                  
    & \textbf{CP-1} & \textbf{CP-2} & \textbf{CP-3} \\
    \specialrule{.1em}{.05em}{.05em}                  
    java      & 150 & 120 & 180 \\ \hline
    ruby      & 220 & 290 & 250 \\ \hline
    postgres  & 320 & 240 & 290 \\ \hline
    python    & 200 & 260 & 180 \\ \hline
    amqp      & 330 & 390 & 285 \\
    \hline  
  \end{tabular}
  \caption{Price for a stack in the given cloud provider}
  \label{tbl:test-service-deployment-cost}
\end{table}

@@

\begin{table}
  \centering
  \begin{tabular}{ c  c  c }
    \specialrule{.1em}{.05em}{.05em} 
    & \multicolumn{2}{c}{\textbf{Solution}} \\
    \cline{2-3}
    \textbf{Instance no} & Cloud-SAP & Carina \\
    \specialrule{.1em}{.05em}{.05em} 
    2 & 198.0 & 158.7 \\ \hline
    3 & 261.72 & 208.1 \\ \hline
    4 & 294.38 & 230.6 \\
    \hline
  \end{tabular}
  \caption{Average deployment time for the service with the various number of VMs used for the whole environment}
  \label{tbl:test-service-deployment-time}
\end{table}
